---
title: "Heidelberg Conference Report"
author: "Teresa Correa & Nicolás Tobar"
date: 14-11-2023
format:
  html:
    code-fold: true
execute: 
  error: false
  warning: false
  message: false
editor: visual
---

# Introduction

The next report contains a first exploration of the digital inclusion 2023 survey, that is oriented for the presentation of Teresa Correa on Heidelberg University. In this case, the exploration is about some constructed index about digital knowledge from the database to explain the variation of attitudes to false information on the internet. The independent variables are:

-   Digital skills index (Van Deuersen)

    -   Operational skills index[^2]
    -   Informative skills index[^3]
    -   Social skills index[^4]
    -   Creative skills index[^5]
    
-   Digital literacy index (Hargittai)[^6]

    -   Social media literacy index
    -   Algorithmic literacy index
    
-   Algorithmic awareness index (Zarouali)[^7]

-   Political polar position \[Categorical\]

[^1]: **On a scale of 1 to 3, where 1 means "Never" and 3 means "Frequently" How often do you feel the following?**

    1.  You feel safe using the internet to find information.

    2.  Feels confident about learning new skills on the internet.

    3.  Feels confident in understanding terms related to the internet

    4.  If I have problems using the internet, I think I could solve them all.

[^2]: **Regarding your skills in handling new technologies, which of the following do you know how to do?**

    1.  I know how to open a file on the computer

    2.  I know how to create an account on a social network

    3.  I know how to download/save a photo I found on the internet.

    4.  I know how to use commands on the keyboard (e.g. ctrl+c to copy and ctrl+v to paste)

    5.  I know how to open a new page in the browser

    6.  I know how to bookmark a web page that interests me.

[^3]: **Regarding your skills in handling new technologies, which of the following do you know how to do?**

    1.  I know how to connect to a wifi (wireless) network

    2.  I know how to find a page I have visited before.

    3.  I sometimes end up browsing websites without knowing how I got there.

    4.  I find many websites confusing in the way they are designed

    5.  I can decide what are the best terms to search for on the internet.

[^4]: **Regarding your skills in handling new technologies, which of the following do you know how to do?**

    1.  I know what kind of information I can and cannot share on the internet.

    2.  I know when I should and should not share information online.

    3.  I take care that the comments and behaviours I engage in online are appropriate to the situation I am in online

    4.  I take care to check if the information I find is up to date.

    5.  I take care to check the trustworthiness of a website.

    6.  I take care to check the information I find on one website against a different website.

[^5]: **Regarding your skills in handling new technologies, which of the following do you know how to do?**

    1.  I know how to create something new from videos/music and photos that already exist.

    2.  I know how to make basic changes to content that others have created

    3.  I know how to design a website (e.g., wordpress)

[^6]: **On a scale of 1 to 5 where 1 means "not at all" and 5 means "very much" How familiar are you with the following computer and internet related terms?**

    Advanced search \[Algorithmic Literacy\]

    PDF

    Wiki

    Favourites

    JPG

    MP4

    5G

    Influencer \[Social media Literacy\]

    Cache \[Algorithmic Literacy\]

    Cookie \[Algorithmic Literacy\]

    Phishing

    Tag \[Social media Literacy\]

    Followers \[Social media Literacy\]

    Privacy Settings \[Algorithmic Literacy\]

    Meme \[Social media Literacy\]

    Youtuber \[Social media Literacy\]

    Hashtag \[Social media Literacy\]

    Gamer

[^7]: To what extent are you aware of the following statements about the presence of algorithms on social media (Facebook, Instagram, TikTok, Twitter) and streaming platforms (Netflix, Disney+)?

    1.  Algorithms are used to recommend me content (videos, photos, movies, series) on social networks and streaming platforms

    2.  Algorithms are used to prioritise certain content (videos, photos, movies, series) over others on social networks and streaming platforms.

    3.  The content (videos, photos, movies, series) that the algorithms recommend to me depends on my behaviour on social networks and streaming platforms.

    4.  The content (videos, photos, movies, series) recommended to me by algorithms depends on the data I provide on social networks and streaming platforms.

    5.  The use of my personal data in the algorithms has consequences for my online privacy.

    6.  The content (videos, photos, movies, series) recommended by algorithms may be subject to human biases such as prejudice or stereotypes.

The items to predict comes from the next question: *"When you surf the internet or use social media, how often have the following situations occurred to you?"*

And the items are:

-   "I have seen or read false or misleading news"
-   "I have believed news that later turned out to be false or misleading"
-   "I have shared information that subsequently turned out to be false or misleading"

# Data description

The table show the different variables, how they were created or calculated, some descriptive statistics and the Cronbach alpha (only for index's). Some advises:

-   Algorithmic awareness index first had 207	missing values (19% of total cases). All of them were recoded as "1" [Not awareness].
-   Political polar position variable is a recodification of 1 [left] - 10 [right] political position scale. Extreme positions of both wings (1,2,3/8,9,10) were recoded as "Polarized" people, center positions (4,5,6,7) were recoded as "Centered" people, and people who don't recognise them with the scale (principally Don't know/ Don't answer) were recoded as "Non-scaled". The last group represent the 55% cases of the sample.
-   Van Deursen's digital skill index is contained totally by the other four index's. Meanwhile, Hargittai's digital literacy index is not totally contained by social media and algorithmic literacy index, because have other items that are not in this scale.
-   All alpha's of mean constructed index's, with at least 95 of confidence, have a score more than 0.90, so the indexs used have internal consistency.

```{r,results='hide',error=FALSE}
# 0. Preparation ----

pacman::p_load(
  tidyverse, #Data manipulation
  haven, #Read sav
  janitor, #Clean names
  ltm, #Cronbach alpha
  skimr, #Descriptive table
  gt, #Render tables
  labelled, #col_labes
  corrplot, #Corrplot
  sjPlot, #Tab models
  labelled, #double manage
  sjmisc, #to_label
  Hmisc)

load("../01_input/02_proc_data/digital_inclusion_2023.RData")

options(digits = 2)

# 1. Index creation ----

# Extreme political position index (Not used)

# raw_2023<-raw_2023 %>% 
 # mutate(i_extreme_politics=case_when(f18%in%c(1,10)~5,
  #                                    f18%in%c(2,9)~4,
   #                                   f18%in%c(3,8)~3,
    #                                  f18%in%c(4,7)~2,
     #                                 f18%in%c(5,6)~1))

# Extreme politization variable

data <- data %>%
         mutate(
          extreme_politization=case_when(f18%in%c(1,2,3,8,9,10)~"[a. Polarized]",
                                         f18%in%c(4,5,6,7)~"[b. Centered]",
                                         f18==99 ~ "[c. Non-scaled]"))

# Anti fake-news sharing scale

data$anti_fake_news <- 
         data %>% 
         mutate_at(.vars=vars(starts_with("c5_")),
                   .funs=list(~ifelse(.==99,NA,.))) %>%
         dplyr::select(c5_4,
                       c5_5,
                       c5_6) %>%
         mutate_all(as.numeric) %>%
         rowMeans(na.rm=T)

# Social media literacy

data$social_media_literacy <- 
            data %>% 
             mutate_at(.vars=vars(c4_12,c4_13,c4_15,c4_16,c4_17,c4_18),
                       .funs=list(~ ifelse(.==99,NA,.))) %>% 
             dplyr::select(c4_12,c4_13,c4_15,c4_16,c4_17,c4_18) %>%
             mutate_all(as.numeric) %>%
             rowMeans(na.rm=T)

# Algorithmic literacy

data$algorithmic_literacy <- 
            data %>% mutate_at(.vars=vars(c4_10,c4_9,c4_14,c4_1,d1),
                               .funs=list(~ifelse(.==99,NA,.))) %>% 
             dplyr::select(c4_12,c4_13,c4_15,c4_16,c4_17,c4_18) %>%
             mutate_all(as.numeric) %>%
             rowMeans(na.rm=T)



# 2. Create alpha objects ----
c1 <-cronbach.alpha(data %>% dplyr::select(starts_with("c1_")) %>%
                      drop_na(), CI=TRUE) #Alpha of index

c2 <-cronbach.alpha(data %>% dplyr::select(starts_with("c2_")) %>%
                      drop_na(), CI=TRUE) #Alpha of index

c4 <- cronbach.alpha(data %>% dplyr::select(starts_with("c4_")) %>%
                       drop_na(), CI=TRUE) #Alpha of index

c4_a <- cronbach.alpha(data %>% 
                       dplyr::select(c4_12,c4_13,c4_15,c4_16,c4_17,c4_18) %>%
                       drop_na(), CI=TRUE)

c4_b <- cronbach.alpha(data %>% 
                       dplyr::select(c4_10,c4_9,c4_14,c4_1,d1) %>%
                       drop_na(), CI=TRUE) #Alpha of index

d2 <- cronbach.alpha(data %>% dplyr::select(starts_with("d2")) %>%
                       drop_na(), CI=TRUE) #Alpha of index

c5_x <- cronbach.alpha(data %>% dplyr::select(c5_4,c5_5,c5_6) %>%
                      drop_na(), CI=TRUE) #Alpha of index

# List of Cronbach's alphas

Cronbach<-c(c1["alpha"], c2["alpha"],NA,NA,NA,NA,NA,
            c4_a["alpha"],c4_b["alpha"],c4["alpha"],d2["alpha"],
            NA,NA,NA,NA,NA,c5_x)

ci<-c(c1["alpha"], c2["alpha"],NA,NA,NA,NA,NA,
            c4_a["alpha"],c4_b["alpha"],c4["alpha"],d2["alpha"],
            NA,NA,NA,NA,NA,c5_x)

```

### Numerical data
```{r,results='asis'}
data %>% 
  dplyr::select(tech_anxiety,
                tech_self_efficacy,
                tech_operational_skills,
                tech_informative_skills,
                tech_social_skills,
                tech_creative_skills,
                digital_skills,
                social_media_literacy,
                algorithmic_literacy,
                digital_literacy,
                algorithmic_awareness,
                social_capital,
                extreme_politization,
                c5_1,c5_2,c5_3,
                anti_fake_news) %>% 
  skim() %>% 
  as.data.frame()%>%
  
  mutate(Label= c("Technological anxiety scale",
                  "Technological Self-efficacy scale",
                  "Technological Operational skills scale [Van Deuersen]",
                  "Technological Informative skills scale [Van Deuersen]",
                  "Technological Social skills scale [Van Deuersen]",
                  "Technological Creative skills scale [Van Deuersen]",
                  "Van Deursen's Technological Digital skills scale (total)",
                  "Social media literacy scale [Hargittai]",
                  "Algorithmic literacy scale [Hargittai]",
                  "Hargittai's Digital literacy scale (total)",
                  "Zarouali's Algorithmic awareness scale",
                  "Social capital",
                  "Extreme politization",
                  "I have seen or read false or misleading news",
                  "I have believed news that later turned out to be false or misleading",
                  "I have shared information that subsequently turned out to be false or misleading",
                  "Anti-fake news actions scale"),
         
         Estimation=c("By means (1 - 3)",
                      "By means (1 - 3)",
                      "Sumative (0 - 6)",
                      "Sumative (0 - 5)",
                      "Sumative (0 - 6)",
                      "Sumative (0 - 3)",
                      "Sumative (0 - 20)",
                      "By means (1 - 5)",
                      "By means (1 - 5)",
                      "By means (1 - 5)",
                      "By means (1 - 5)",
                      "Sumative (1-13)",
                      "Categorical",
                      "Raw data",
                      "Raw data",
                      "Raw data",
                      "By means (1 - 5)"))%>%
    dplyr::select(Variable=skim_variable,
                Label,
                Estimation,
                Mean=numeric.mean,
                SD=numeric.sd,
                N_Missing=n_missing,
                Complete_rate=complete_rate,
                Hist=numeric.hist) %>%
  mutate(Mean=round(Mean,2),
         SD=round(SD,2),
         Complete_rate=paste0(round(Complete_rate*100,2),"%"),
         Cronbach=Cronbach[1:17],
         "C.I. [2.5%;97.5%]"=ci[1:17])%>%

  gt() %>%
  sub_missing(missing_text = "")
```


# Correlations

### Table of correlations

```{r, results='markup'}

model_data <- data %>% dplyr::select(
                tech_anxiety,
                tech_self_efficacy,
                tech_operational_skills,
                tech_informative_skills,
                tech_social_skills,
                tech_creative_skills,
                digital_skills,
                social_media_literacy,
                algorithmic_literacy,
                digital_literacy,
                algorithmic_awareness,
                social_capital,
                extreme_politization,
                c5_1,c5_2,c5_3,
                anti_fake_news, 
                gender=a1,
                age=a2,
                ses=nse,
                tipo_zona) %>%
              mutate(gender=ifelse(gender==2,1,0),
                     tipo_zona=ifelse(tipo_zona==2,0,1)) %>%
              mutate_all(as.numeric)%>%
              mutate_all(~ifelse(.==99,NA,.))
```
::: panel-tabset

### Table {.scrollable}

```{r, results='markup'}
var_label(model_data)<-c("Technological anxiety scale",
                  "Technological Self-efficacy scale",
                  "Technological Operational skills scale [Van Deuersen]",
                  "Technological Informative skills scale [Van Deuersen]",
                  "Technological Social skills scale [Van Deuersen]",
                  "Technological Creative skills scale [Van Deuersen]",
                  "Van Deursen's Technological Digital skills scale (total)",
                  "Social media literacy scale [Hargittai]",
                  "Algorithmic literacy scale [Hargittai]",
                  "Hargittai's Digital literacy scale (total)",
                  "Zarouali's Algorithmic awareness scale",
                  "Social capital",
                  "Extreme politization",
                  "I have seen or read false or misleading news",
                  "I have believed news that later turned out to be false or misleading",
                  "I have shared information that subsequently turned out to be false or misleading",
                  "Anti-fake news actions scale",
                  "Gender (Women=1)",
                  "Age",
                  "Socioeconomical Status",
                  "Tipo de zona(Rural=1)")

#Eliminar categóricas
cor_data <- model_data %>% dplyr::select(-c(age,ses,gender,
                                            extreme_politization,tipo_zona))

sjPlot::tab_corr(cor_data, na.deletion = "pairwise",
                 corr.method = "pearson", title = "Correlations", 
                 show.p = TRUE, digits = 2)

```

### Summary

```{r}
corrplot(cor(cor_data, use = "pairwise.complete.obs",
    method = "pearson"), 
    method = 'circle', type = 'lower', 
    order = 'AOE', diag=FALSE)

```
:::

# Models

::: panel-tabset
### Algorithmic awareness + control

```{r}
c5_1_a<-lm(c5_1 ~ algorithmic_awareness + tipo_zona + age + gender + ses, data = model_data)
c5_2_a<-lm(c5_2 ~ algorithmic_awareness + tipo_zona + age + gender + ses, data = model_data)
c5_3_a<-lm(c5_3 ~ algorithmic_awareness + tipo_zona + age + gender + ses, data = model_data)
c5_x_a<-lm(anti_fake_news ~ algorithmic_awareness + tipo_zona + age + gender + ses, data = model_data)

tab_model(c5_1_a,c5_2_a,c5_3_a,c5_x_a,
          show.ci = FALSE, auto.label = TRUE,
          p.style = "stars",collapse.se = TRUE,
          show.re.var = FALSE,show.icc = FALSE,
          show.obs = TRUE,show.ngroups = FALSE)
```

### Digital literacy + control

```{r}
c5_1_b<-lm(c5_1 ~ digital_literacy + tipo_zona + age + gender + ses, data = model_data)
c5_2_b<-lm(c5_2 ~ digital_literacy + tipo_zona + age + gender + ses, data = model_data)
c5_3_b<-lm(c5_3 ~ digital_literacy + tipo_zona + age + gender + ses, data = model_data)
c5_x_b<-lm(anti_fake_news ~ digital_literacy + tipo_zona + age + gender + ses, data = model_data)
tab_model(c5_1_b, c5_2_b,c5_3_b,c5_x_b, 
          show.ci = FALSE, auto.label = TRUE,
          p.style = "stars",collapse.se = TRUE,
          show.re.var = FALSE,show.icc = FALSE,
          show.obs = TRUE,show.ngroups = FALSE)
```

### Digital skills + control

```{r}
c5_1_c<-lm(c5_1 ~ digital_skills + tipo_zona + age + gender + ses, data = model_data)
c5_2_c<-lm(c5_2 ~ digital_skills + tipo_zona + age + gender + ses, data = model_data)
c5_3_c<-lm(c5_3 ~ digital_skills + tipo_zona + age + gender + ses, data = model_data)
c5_x_c<-lm(anti_fake_news ~ digital_skills + tipo_zona + age + gender + ses, data = model_data)

tab_model(c5_1_c, c5_2_c,c5_3_c,c5_x_c, 
          show.ci = FALSE, auto.label = TRUE,
          p.style = "stars",collapse.se = TRUE,
          show.re.var = FALSE,show.icc = FALSE,
          show.obs = TRUE,show.ngroups = FALSE)
```
:::

### Social media frequency use model

```{r}

social_media_data<-data%>%dplyr::select(    Youtube=b12_1,
                                            Facebook=b12_2,
                                            Twitter=b12_3,
                                            Instagram=b12_4,
                                            Whatsapp=b12_5,
                                            TikTok=b12_6)%>%
                    replace(is.na(.), 0)%>% #Missing values as non-registered users
                    mutate_all(~ifelse(.==99,NA,.))

  
var_label(social_media_data) <- c("Youtube frequency of use",
                                   "Facebook frequency of use",
                                   "Twitter frequency of use",
                                   "Instagram frequency of use",
                                   "Whatsapp frequency of use",
                                   "TikTok frequency of use")
                         
model_data <- cbind(model_data,social_media_data)


c5_1_d<-lm(c5_1 ~ age + gender + ses + tipo_zona +
           algorithmic_awareness +
           Youtube + Facebook + Twitter + Instagram + Whatsapp + TikTok,
           data = model_data)
c5_2_d<-lm(c5_2 ~ age + gender + ses + tipo_zona +
           algorithmic_awareness +
           Youtube + Facebook + Twitter + Instagram + Whatsapp + TikTok,
           data = model_data)
c5_3_d<-lm(c5_3 ~ age + gender + ses + tipo_zona +
           algorithmic_awareness +
           Youtube + Facebook + Twitter + Instagram + Whatsapp + TikTok,
           data = model_data)
c5_x_d<-lm(anti_fake_news ~ age + gender + ses + tipo_zona +
           algorithmic_awareness +
           Youtube + Facebook + Twitter + Instagram + Whatsapp + TikTok,
           data = model_data)

tab_model(c5_1_d, c5_2_d,c5_3_d,c5_x_d, 
          show.ci = FALSE, auto.label = TRUE,
          p.style = "stars",collapse.se = TRUE,
          show.re.var = FALSE,show.icc = FALSE,
          show.obs = TRUE,show.ngroups = FALSE)
```


