---
title: "Heidelberg Conference Report"
author: "Teresa Correa & Nicolás Tobar"
date: 14-11-2023
format:
  html:
    code-fold: true
execute: 
  error: false
  warning: false
  message: false
editor: visual
---

# Introduction

The next report contains a first exploration of the digital inclusion 2023 survey, that is oriented for the presentation of Teresa Correa on Heidelberg University. In this case, the exploration is about some constructed index about digital knowledge from the database to explain the variation of attitudes to false information on the internet. The independent variables are:

-   Self-efficacy index[^1]

-   Digital skills index (Van Deuersen)

    -   Operational skills index[^2]
    -   Informative skills index[^3]
    -   Social skills index[^4]
    -   Creative skills index[^5]
    
-   Digital literacy index (Hargittai)[^6]

    -   Social media literacy index
    -   Algorithmic literacy index
    
-   Algorithmic awareness index (Zarouali)[^7]

-   Political polar position \[Categorical\]

[^1]: **On a scale of 1 to 3, where 1 means "Never" and 3 means "Frequently" How often do you feel the following?**

    1.  You feel safe using the internet to find information.

    2.  Feels confident about learning new skills on the internet.

    3.  Feels confident in understanding terms related to the internet

    4.  If I have problems using the internet, I think I could solve them all.

[^2]: **Regarding your skills in handling new technologies, which of the following do you know how to do?**

    1.  I know how to open a file on the computer

    2.  I know how to create an account on a social network

    3.  I know how to download/save a photo I found on the internet.

    4.  I know how to use commands on the keyboard (e.g. ctrl+c to copy and ctrl+v to paste)

    5.  I know how to open a new page in the browser

    6.  I know how to bookmark a web page that interests me.

[^3]: **Regarding your skills in handling new technologies, which of the following do you know how to do?**

    1.  I know how to connect to a wifi (wireless) network

    2.  I know how to find a page I have visited before.

    3.  I sometimes end up browsing websites without knowing how I got there.

    4.  I find many websites confusing in the way they are designed

    5.  I can decide what are the best terms to search for on the internet.

[^4]: **Regarding your skills in handling new technologies, which of the following do you know how to do?**

    1.  I know what kind of information I can and cannot share on the internet.

    2.  I know when I should and should not share information online.

    3.  I take care that the comments and behaviours I engage in online are appropriate to the situation I am in online

    4.  I take care to check if the information I find is up to date.

    5.  I take care to check the trustworthiness of a website.

    6.  I take care to check the information I find on one website against a different website.

[^5]: **Regarding your skills in handling new technologies, which of the following do you know how to do?**

    1.  I know how to create something new from videos/music and photos that already exist.

    2.  I know how to make basic changes to content that others have created

    3.  I know how to design a website (e.g., wordpress)

[^6]: **On a scale of 1 to 5 where 1 means "not at all" and 5 means "very much" How familiar are you with the following computer and internet related terms?**

    Advanced search \[Algorithmic Literacy\]

    PDF

    Wiki

    Favourites

    JPG

    MP4

    5G

    Influencer \[Social media Literacy\]

    Cache \[Algorithmic Literacy\]

    Cookie \[Algorithmic Literacy\]

    Phishing

    Tag \[Social media Literacy\]

    Followers \[Social media Literacy\]

    Privacy Settings \[Algorithmic Literacy\]

    Meme \[Social media Literacy\]

    Youtuber \[Social media Literacy\]

    Hashtag \[Social media Literacy\]

    Gamer

[^7]: To what extent are you aware of the following statements about the presence of algorithms on social media (Facebook, Instagram, TikTok, Twitter) and streaming platforms (Netflix, Disney+)?

    1.  Algorithms are used to recommend me content (videos, photos, movies, series) on social networks and streaming platforms

    2.  Algorithms are used to prioritise certain content (videos, photos, movies, series) over others on social networks and streaming platforms.

    3.  The content (videos, photos, movies, series) that the algorithms recommend to me depends on my behaviour on social networks and streaming platforms.

    4.  The content (videos, photos, movies, series) recommended to me by algorithms depends on the data I provide on social networks and streaming platforms.

    5.  The use of my personal data in the algorithms has consequences for my online privacy.

    6.  The content (videos, photos, movies, series) recommended by algorithms may be subject to human biases such as prejudice or stereotypes.

The items to predict comes from the next question: *"When you surf the internet or use social media, how often have the following situations occurred to you?"*

And the items are:

-   "I have seen or read false or misleading news"
-   "I have believed news that later turned out to be false or misleading"
-   "I have shared information that subsequently turned out to be false or misleading"

# Data description

The table show the different variables, how they were created or calculated, some descriptive statistics and the Cronbach alpha (only for index's). Some advises:

-   Algorithmic awareness index first had 207	missing values (19% of total cases). All of them were recoded as "1" [Not awareness].
-   Political polar position variable is a recodification of 1 [left] - 10 [right] political position scale. Extreme positions of both wings (1,2,3/8,9,10) were recoded as "Polarized" people, center positions (4,5,6,7) were recoded as "Centered" people, and people who don't recognise them with the scale (principally Don't know/ Don't answer) were recoded as "Non-scaled". The last group represent the 55% cases of the sample.
-   Van Deursen's digital skill index is contained totally by the other four index's. Meanwhile, Hargittai's digital literacy index is not totally contained by social media and algorithmic literacy index, because have other items that are not in this scale.
-   All alpha's of mean constructed index's, with at least 95 of confidence, have a score more than 0.90, so the indexs used have internal consistency.

```{r,results='hide',error=FALSE}
# 0. Preparation ----

pacman::p_load(
  tidyverse, #Data manipulation
  haven, #Read sav
  janitor, #Clean names
  ltm, #Cronbach alpha
  skimr, #Descriptive table
  gt, #Render tables
  labelled, #col_labes
  corrplot, #Corrplot
  sjPlot, #Tab models
  labelled, #double manage
  sjmisc #to_label
  )

raw_2023 <- read_sav("../01_input/01_raw_data/2023_survey_raw.sav") %>% clean_names()

options(digits = 2)

# 1. Index creation ----

# Technological Self-efficacy


raw_2023 <- raw_2023 %>% mutate_at(.vars=vars(starts_with("c2_")),
                                   .funs=list(~ifelse(.==99,NA,.)))

c2 <-cronbach.alpha(raw_2023 %>% dplyr::select(starts_with("c2_")) %>%
                 drop_na(), CI=TRUE) #Alpha of index

raw_2023$i_tech_self_efficacy <- raw_2023 %>% dplyr::select(starts_with("c2_"))%>%
                                   mutate_all(as.integer)%>%rowMeans(na.rm=T)

# Digital skills

raw_2023 <- raw_2023 %>% mutate_at(.vars=vars(starts_with("c3_")),
                                   .funs=list(~ifelse(.==2,0,.)))
## Operational skills
raw_2023$i_operational_skills <- raw_2023 %>% dplyr::select(starts_with("c3_1"))%>%
                               mutate(across(everything(),~ifelse(.==99,NA,.)))%>%
                               mutate_all(as.integer)%>% rowSums(na.rm = T)

## Informative skills
raw_2023$i_informative_skills <- raw_2023 %>% dplyr::select(starts_with("c3_2"))%>%
                               mutate(across(everything(),~ifelse(.==99,NA,.)))%>%
                               mutate_all(as.integer)%>% rowSums(na.rm = T)

## Social skills
raw_2023$i_social_skills <- raw_2023 %>% dplyr::select(starts_with("c3_3"))%>%
                          mutate(across(everything(),~ifelse(.==99,1,.)))%>%
                          mutate_all(as.integer)%>% rowSums(na.rm = T)


## Creative skills
raw_2023$i_creative_skills <- raw_2023 %>% dplyr::select(starts_with("c3_4"))%>%
                            mutate(across(everything(),~ifelse(.==99,NA,.)))%>%
                            mutate_all(as.integer)%>% rowSums(na.rm = T)


## Digital skills (total)
raw_2023$i_digital_skills <- raw_2023$operational_skills <- raw_2023 %>% dplyr::select(starts_with("c3"))%>%
                           mutate(across(everything(),~ifelse(.==99,NA,.)))%>%
                           mutate_all(as.integer)%>% rowSums(na.rm = T)

# Digital Literacy

## Social media literacy

raw_2023 <- raw_2023 %>% mutate_at(.vars=vars(c4_12,c4_13,c4_15,c4_16,c4_17,c4_18),
                                   .funs=list(~ ifelse(.==99,NA,.)))

c4_a <- cronbach.alpha(raw_2023 %>% dplyr::select(c4_12,c4_13,c4_15,c4_16,c4_17,c4_18) %>%
                 drop_na(), CI=TRUE) #Alpha of index

raw_2023$i_social_media_literacy <- raw_2023 %>% 
  dplyr::select(c4_12,c4_13,c4_15,c4_16,c4_17,c4_18)%>%
  mutate_all(as.integer)%>%rowMeans(na.rm=T)

## Algorithmic literacy

raw_2023 <- raw_2023 %>% mutate_at(.vars=vars(c4_10,c4_9,c4_14,c4_1,d1),
                                   .funs=list(~ifelse(.==99,NA,.)))

c4_b <- cronbach.alpha(raw_2023 %>% dplyr::select(c4_10,c4_9,c4_14,c4_1,d1) %>%
                 drop_na(), CI=TRUE) #Alpha of index

raw_2023$i_algorithmic_literacy <- raw_2023 %>% dplyr::select(starts_with("c4_"))%>%
  mutate_all(as.integer)%>%rowMeans(na.rm=T)

## Digital literacy (total)

raw_2023 <- raw_2023 %>% mutate(across(starts_with("c4_"),~ifelse(.==99,NA,.)))

c4 <- cronbach.alpha(raw_2023 %>% dplyr::select(starts_with("c4_")) %>%
                 drop_na(), CI=TRUE) #Alpha of index

raw_2023$i_digital_literacy <- raw_2023 %>% dplyr::select(starts_with("c4_"))%>%
                             mutate_all(as.integer)%>%rowMeans(na.rm=T)

# Algorithmic awareness

raw_2023 <- raw_2023 %>% mutate(across(starts_with("d2"),~ifelse(.==99,1,.))) #NS-NR as non-awareness

d2 <- cronbach.alpha(raw_2023 %>% dplyr::select(starts_with("d2")) %>%
                 drop_na(), CI=TRUE) #Alpha of index

raw_2023$i_algorithmic_awareness <- raw_2023 %>% dplyr::select(starts_with("d2"))%>%
                             mutate_all(as.integer)%>%rowMeans(na.rm=T)

# Extreme political position index

# raw_2023<-raw_2023 %>% 
 # mutate(i_extreme_politics=case_when(f18%in%c(1,10)~5,
  #                                    f18%in%c(2,9)~4,
   #                                   f18%in%c(3,8)~3,
    #                                  f18%in%c(4,7)~2,
     #                                 f18%in%c(5,6)~1))

# Extreme politization variable

raw_2023 <- raw_2023 %>%
            mutate(
              extreme_politization=case_when(f18%in%c(1,2,3,8,9,10)~"[a. Polarized]",
                                             f18%in%c(4,5,6,7)~"[b. Centered]",
                                             f18==99 ~ "[c. Non-scaled]"))

# List of Cronbach's alphas

Cronbach<-c(c2["alpha"],NA,NA,NA,NA,
  c4_a["alpha"],c4_b["alpha"],c4["alpha"],d2["alpha"],NA,NA,NA,NA)

ci<-c(c2["ci"],NA,NA,NA,NA,
            c4_a["ci"],c4_b["ci"],c4["ci"],d2["ci"],NA,NA,NA,NA)

```

### Numerical data
```{r,results='asis'}
raw_2023 %>% dplyr::select(starts_with(c("i_")),c5_1,c5_2,c5_3) %>% 
  mutate_all(~ifelse(.==99,NA,.)) %>%
  skim() %>% as.data.frame()%>%
  mutate(Label= c("Self-efficacy index",
                  "Operational skills index [Van Deuersen]",
                  "Informative skills index [Van Deuersen]",
                  "Social skills index [Van Deuersen]",
                  "Creative skills index [Van Deuersen]",
                  "Van Deursen's Digital skills index (total)",
                  "Social media literacy index [Hargittai]",
                  "Algorithmic literacy index [Hargittai]",
                  "Hargittai's Digital literacy index (total)",
                  "Zarouali's Algorithmic awareness index",
                  "I have seen or read false or misleading news",
                  "I have believed news that later turned out to be false or misleading",
                  "I have shared information that subsequently turned out to be false or misleading"),
         Estimation=c("By means (1 - 3)",
                      "Sumative (0 - 6)",
                      "Sumative (0 - 5)",
                      "Sumative (0 - 6)",
                      "Sumative (0 - 3)",
                      "Sumative (0 - 20)",
                      "By means (1 - 5)",
                      "By means (1 - 5)",
                      "By means (1 - 5)",
                      "By means (1 - 5)",
                      "Raw data",
                      "Raw data",
                      "Raw data"))%>%
    dplyr::select(Variable=skim_variable,
                Label,
                Estimation,
                Mean=numeric.mean,
                SD=numeric.sd,
                N_Missing=n_missing,
                Complete_rate=complete_rate,
                Hist=numeric.hist) %>%
  mutate(Mean=round(Mean,2),
         SD=round(SD,2),
         Complete_rate=paste0(round(Complete_rate*100,2),"%"),
         Cronbach=Cronbach,
         "C.I. [2.5%;97.5%]"=ci)%>%

  gt() %>%
  sub_missing(missing_text = "")
```


# Correlations

About the relationships between variables, we see all the dependent variables have negative correlation with all the index's. In other words, more is the knowledge about digital technologies, less are the probabilities of encountering, believe or share fake news on the web. But the effect size of all indexs with fake news network experiences are slow; don't overpass 0.25 in all cases, so probably this could change if variance is controlled by other variables.

Another observations:
-   All digital indexs have strong positive correlation between them. Probably could be colineality. The same with fake new experience items.
-   Age is the most related variable with the indexs. Have a negative strong effect with all of them.
-   Gender effects are non-significative.
-   Socioeconomic status have a positive correlation with digital indexs. More the status, more the knowledge.

*Political polar position was eliminated because is categorical data*

::: panel-tabset
### Visual summary

```{r, results='markup'}

model_data <- raw_2023 %>% dplyr::select(starts_with(c("i_")),c5_1,c5_2,c5_3,
                                         gender=a1,age=a2,ses=nse)%>%
              mutate(gender=ifelse(gender==2,1,0))%>%
              mutate_all(as.numeric)

corr_matrix<-cor(model_data%>%
                   drop_na())

testRes = cor.mtest(model_data%>%
                      drop_na(), conf.level = 0.95)


corrplot(corr_matrix, method = 'circle', type = 'lower',p.mat = testRes$p, insig = 'blank',order = 'AOE', diag=FALSE)


```

### Table {.scrollable}

```{r, results='markup'}
model_data <- model_data %>%
  mutate_all(~ifelse(.==99,NA,.))

var_label(model_data)<-c("Self-efficacy index",
                  "Operational skills index [Van Deuersen]",
                  "Informative skills index [Van Deuersen]",
                  "Social skills index [Van Deuersen]",
                  "Creative skills index [Van Deuersen]",
                  "Van Deursen's Digital skills index (total)",
                  "Social media literacy index [Hargittai]",
                  "Algorithmic literacy index [Hargittai]",
                  "Hargittai's Digital literacy index (total)",
                  "Zarouali's Algorithmic awareness index",
                  "I have seen or read false or misleading news",
                  "I have believed news that later turned out to be false or misleading",
                  "I have shared information that subsequently turned out to be false or misleading",
                     "Gender (Women=1)",
                     "Age",
                     "Socioeconomical Status")

sjPlot::tab_corr(model_data, na.deletion = "pairwise",
corr.method = "pearson", title = "Title of Table", show.p = TRUE, digits = 2)

```
:::

# Models

In the next dashboard you can explore three index's multivariate regression models. The first only have Algorithmic awareness as an importante predictor (Zarouali index), the second only digital literacy (Hargittai index), and the third one use Van Deursen's digital skills scale as the independent variable. All of them controlled by age, gender and socioeconomic status.

Results show all of them have negative effect to the three dependent variables. In other words, controlling by sociodemographic characteristics, if the frequency of encountering, believe or share fake news on the web increases one point, then the algorithmic awareness decrease by 1 to 1.40 points, digital literacy decrease by 2 to 2.40 points and digital skills  decrease by 0.70-0.80 points. 

In other words, as people is less prepared in the digital world, more is the probability of recognise seeing, believing or sharing fake news. But the model have a little explicative power, considering none of them have more than a 0.08 square R.

::: panel-tabset
### Algorithmic awareness + control

```{r}
c5_1_a<-lm(c5_1 ~ i_algorithmic_awareness + age + gender + ses, data = model_data)
c5_2_a<-lm(c5_2 ~ i_algorithmic_awareness + age + gender + ses, data = model_data)
c5_3_a<-lm(c5_3 ~ i_algorithmic_awareness + age + gender + ses, data = model_data)

tab_model(c5_1_a, c5_2_a,c5_3_a, 
          show.ci = FALSE, auto.label = TRUE,
          p.style = "stars",collapse.se = TRUE,
          show.re.var = FALSE,show.icc = FALSE,
          show.obs = TRUE,show.ngroups = FALSE)
```

### Digital literacy + control

```{r}
c5_1_b<-lm(c5_1 ~ i_digital_literacy + age + gender + ses, data = model_data)
c5_2_b<-lm(c5_2 ~ i_digital_literacy + age + gender + ses, data = model_data)
c5_3_b<-lm(c5_3 ~ i_digital_literacy + age + gender + ses, data = model_data)

tab_model(c5_1_b, c5_2_b,c5_3_b, 
          show.ci = FALSE, auto.label = TRUE,
          p.style = "stars",collapse.se = TRUE,
          show.re.var = FALSE,show.icc = FALSE,
          show.obs = TRUE,show.ngroups = FALSE)
```

### Digital skills + control

```{r}
c5_1_c<-lm(c5_1 ~ i_digital_skills + age + gender + ses, data = model_data)
c5_2_c<-lm(c5_2 ~ i_digital_skills + age + gender + ses, data = model_data)
c5_3_c<-lm(c5_3 ~  i_digital_skills + age + gender + ses, data = model_data)

tab_model(c5_1_c, c5_2_c,c5_3_c, 
          show.ci = FALSE, auto.label = TRUE,
          p.style = "stars",collapse.se = TRUE,
          show.re.var = FALSE,show.icc = FALSE,
          show.obs = TRUE,show.ngroups = FALSE)
```
:::

### Social media frequency use model

To construct a more explicative model, the exploratory analysis finish with an integrative model, which add social media frequency use, breaks down dimensions of Van Deursen's index and add self efficacy and extreme politization variables.

Results show operative skills is not an important dimension for fake news experience, because have little and non-significative effects. But social digital skills get all significant, strong and negative coefficients. So less the capacities to distinct false information, more the frequency of see, believe and share fake news. 

Algorithmic awareness obtained non-significant negative coefficients. Without confidence, data show people with less awareness of how the social medias select the information to the user tends to encounter, believe and share more fake news. 

In extreme politization the reference category is polarized people, in other words, ones who recognise the left-right scale and select one of the wings of the scale. Centered people tends to see, believe and share more fake news than extreme politized, but people who do not recognise them in the right-wing scale tends to be the less fake news believers and sharers by a big distance from polarized people. This are non-significant results.

About social media frequency use, all significant coefficients are positive (facebook and instagram). Also in non-significant whatsapp coefficients. So, we can say that more the frequency of use of these three apps, more the exposure to fake news and the probability to share and believe them. In instagram this tendencies is more strong than in the other apps mentioned.

Important to mention: Gender categorical coefficients expose that, in mean, women have between 3.8 less points than men in frequency of seeing fake news, 3.4 less in frequency of believing and 2.5 less in sharing fake news. with confidence, womens are less related to false informativon propagation on the internet.

In summary, with confidence, we can say social digital skills and technological self efficacy are necessary to prevent fake news propagation, but the most explicative factor to be a fake new believer/sharer is the frequency of use of social medias, especially in instagram, and gender. Also, there's not many differences between centered or polarized politized people, but there is between politized and non politized people.

```{r}

social_media_data<-raw_2023%>%dplyr::select(Facebook=b12_2,
                                            Twitter=b12_3,
                                            Instagram=b12_4,
                                            Whatsapp=b12_5,
                                            TikTok=b12_6,
                                            extreme_politization)%>%
                    replace(is.na(.), 1) #Missing values as non-frequent users

var_labels(social_media_data) <- c("Facebook frequency of use",
                                   "Twitter frequency of use",
                                   "Instagram frequency of use",
                                   "Whatsapp frequency of use",
                                   "TikTok frequency of use")
                         
model_data <- cbind(model_data,social_media_data)


c5_1_d<-lm(c5_1 ~ i_operational_skills + i_social_skills + i_algorithmic_awareness +
             extreme_politization + i_tech_self_efficacy +
             Facebook + Twitter + Instagram + Whatsapp + TikTok +
             age + gender + ses, data = model_data)
c5_2_d<-lm(c5_2 ~ i_operational_skills + i_social_skills + i_algorithmic_awareness +
             extreme_politization + i_tech_self_efficacy +
             Facebook + Twitter + Instagram + Whatsapp + TikTok +
             age + gender + ses, data = model_data)
c5_3_d<-lm(c5_3 ~  i_operational_skills + i_social_skills + i_algorithmic_awareness +
             extreme_politization + i_tech_self_efficacy +
             Facebook + Twitter + Instagram + Whatsapp + TikTok +
             age + gender + ses, data = model_data)

tab_model(c5_1_d, c5_2_d,c5_3_d, 
          show.ci = FALSE, auto.label = TRUE,
          p.style = "stars",collapse.se = TRUE,
          show.re.var = FALSE,show.icc = FALSE,
          show.obs = TRUE,show.ngroups = FALSE)
```


