---
title: "ICA 2026"
author: "Teresa Correa, Catalina Farías & Nicolás Tobar"
date: 14-11-2023
format:
  html:
    code-fold: true
execute: 
  error: false
  warning: false
  message: false
editor: visual
---

```{r intro}
# ---- PACKAGE MANAGEMENT ----
# This block loads (and installs if necessary) all required packages
if (!require("pacman")) install.packages("pacman")

pacman::p_load(
  tidyverse,    # data wrangling (dplyr, ggplot2, etc.)
  haven,        # import SPSS/Stata/SAS data
  labelled,     # manage variable and value labels
  psych,        # reliability tests (Cronbach's alpha)
  sjlabelled,   # labeling utilities compatible with tidyverse
  car,          # regression diagnostics (VIF, etc.)
  lmtest,       # regression tests
  sandwich,     # lm specifications
  Hmisc,        # Correlation matrix
  scales,       # normalization and rescaling
  dplyr,        # ensure dplyr functions are active
  psych,        # cronbach alpha
  readr,        # reading csv or txt data
  tidyr,        # data tidying
  stringr,      # string handling
  sjPlot,       # Plot analysis
  ggplot2,      # data visualization
  knitr,        # Markdown knit
  KableExtra,    # Personalize design knit
  flextable     # export tables 
)

#Open data
load("~/GitHub/milenio_nudos/2023_digital_inclusion/01_input/02_proc_data/digital_inclusion_2023.RData")
```

```{r proc demographics}
# ---- SOCIODEMOGRAPHIC VARIABLES ----
data <- data %>%
  mutate(
    # Gender: 0 = male, 1 = female
    a1 = ifelse(a1 == 2, 1,
         ifelse(a1 == 1, 0, NA)),

    gender = factor(a1,
                    levels = c(0, 1),
                    labels = c("Male", "Female")),
    
    # Change age variable name
    age = a2,
    
    # Type of residence: 1 = urban, 2 = ral
    residence = case_when(
      tipo_zona == 1 ~ "Urban",
      tipo_zona == 2 ~ "Rural",
      TRUE ~ NA_character_
    ),
    residence = factor(residence, levels = c("Urban", "Rural"))
  )

# Innovative personality
innovative_variables_2023 <- data %>% dplyr::select(starts_with("f2_"))%>%
                             mutate(across(everything(),~case_when(.==1~4,
                                                          .==2~3,
                                                          .==3~2,
                                                          .==4~1,
                                                          TRUE ~ NA_real_)))

data$innovative_personality <- innovative_variables_2023 %>% 
  mutate_all(as.integer)%>%
  rowMeans(na.rm=T)

#Social network
data$soc_net <- data %>% 
  dplyr::select(starts_with("f6_")) %>%
  mutate_all(as.integer) %>%
  mutate(across(everything(),~case_when(.==2~0,
                                        .==1~1,
                                        TRUE~NA_real_)))%>%
  rowSums(na.rm=T)

#Childs in house (taken from raw_data)
raw_2023 <- read_sav("../01_input/01_raw_data/2023_survey_raw.sav") %>% 
  janitor::clean_names()

data$childs <- raw_2023 %>% 
  dplyr::select(starts_with("edad")) %>%
  mutate_all(~case_when(.<=18~1,.>18~0,TRUE~NA_real_)) %>%
  rowSums(.,na.rm = T)%>%as.numeric()

```

```{r proc digital skills}

# ---- DIGITAL SKILLS INDICES (van Deursen, 2014; 2020) ----
# Each subscale is built from items in battery C3 following your structure.

# Define item groups
operational_items <- c("c3_1_1", "c3_1_2", "c3_1_3", "c3_1_4", "c3_1_5", "c3_1_6")
informative_items <- c("c3_2_1", "c3_2_2", "c3_2_3", "c3_2_4", "c3_2_5")
social_items      <- c("c3_3_1", "c3_3_2", "c3_3_3", "c3_3_4", "c3_3_5", "c3_3_6")
creative_items    <- c("c3_4_1", "c3_4_2", "c3_4_3")

# ---- Ensure C3 items are numeric ----
data <- data %>%
  # Convertir items c3 a 0/1 y reemplazar 99 por NA
  mutate(across(starts_with("c3"), ~ case_when(
    . == 1 ~ 1,
    . == 2 ~ 0,
    . == 99 ~ NA_integer_,
    TRUE ~ NA_integer_
  ))) %>%
  # Asegurar que las sub-dimensiones sean numéricas
  mutate(across(all_of(c(operational_items, informative_items, social_items, creative_items)), ~ as.numeric(.)))


# ---- SUMMATIVE INDICES (raw sums) with NA-if-all-missing protection ----
data <- data %>%
  mutate(
    # Operational (sum of c3_1_*)
    op_n = rowSums(!is.na(select(., all_of(operational_items)))),
    op_sum = rowSums(select(., all_of(operational_items)), na.rm = TRUE),
    tech_operational_skills_raw = if_else(op_n == 0, NA_real_, op_sum),

    # Informative (sum of c3_2_*)
    inf_n = rowSums(!is.na(select(., all_of(informative_items)))),
    inf_sum = rowSums(select(., all_of(informative_items)), na.rm = TRUE),
    tech_informative_skills_raw = if_else(inf_n == 0, NA_real_, inf_sum),

    # Social (sum of c3_3_*)
    soc_n = rowSums(!is.na(select(., all_of(social_items)))),
    soc_sum = rowSums(select(., all_of(social_items)), na.rm = TRUE),
    tech_social_skills_raw = if_else(soc_n == 0, NA_real_, soc_sum),

    # Creative (sum of c3_4_*)
    cre_n = rowSums(!is.na(select(., all_of(creative_items)))),
    cre_sum = rowSums(select(., all_of(creative_items)), na.rm = TRUE),
    tech_creative_skills_raw = if_else(cre_n == 0, NA_real_, cre_sum)
  )

# ---- NORMALIZATION to 0-1 (observed min-max) ----
# keep normalize function (observed min-max)
normalize <- function(x) (x - min(x, na.rm = TRUE)) / 
                         (max(x, na.rm = TRUE) - min(x, na.rm = TRUE))

data <- data %>%
  mutate(
    tech_operational_skills = normalize(tech_operational_skills_raw),
    tech_informative_skills = normalize(tech_informative_skills_raw),
    tech_social_skills      = normalize(tech_social_skills_raw),
    tech_creative_skills    = normalize(tech_creative_skills_raw)
  )

# ---- RELIABILITY CHECK (OPTIONAL) ----
# Cronbach’s alpha for each subscale (recommended for reporting)
#library(psych)

#alpha_operational <- psych::alpha(data %>% select(all_of(operational_items)))
#alpha_informative <- psych::alpha(data %>% select(all_of(informative_items)))
#alpha_social      <- psych::alpha(data %>% select(all_of(social_items)))
#alpha_creative    <- psych::alpha(data %>% select(all_of(creative_items)))

#cat("\nCronbach's alpha coefficients:\n")
#cat("Operational skills: ", round(alpha_operational$total$raw_alpha, 2), "\n")
#cat("Informative skills: ", round(alpha_informative$total$raw_alpha, 2), "\n")
#cat("Social skills: ", round(alpha_social$total$raw_alpha, 2), "\n")
#cat("Creative skills: ", round(alpha_creative$total$raw_alpha, 2), "\n")

```

```{r proc algorithmic awareness}
# ---- ALGORITHMIC AWARENESS INDEX (MEAN SCALE) ----
# Based on items from battery D2 (Algorithmic Media Content Awareness - AMCA)

# 1. Convert all D2 items to numeric
data <- data %>%
  mutate(across(starts_with("d2"), as.numeric))%>%
  mutate(across(starts_with("d2"), ~ ifelse(. == 99, 1, .)))

# 2. Compute the mean index for algorithmic awareness
#    The index represents the average awareness level across all D2 items
data <- data %>%
  mutate(
    algorithmic_awareness = rowMeans(select(., starts_with("d2")), na.rm = TRUE)
  )

# 3. Normalize to 0–1 range (optional, for comparability with other indices)
normalize <- function(x) (x - min(x, na.rm = TRUE)) / 
                         (max(x, na.rm = TRUE) - min(x, na.rm = TRUE))

data <- data %>%
  mutate(
    algorithmic_awareness = normalize(algorithmic_awareness)
  )

# 4. Reliability check (Cronbach’s alpha)
awareness_items <- names(select(data, starts_with("d2")))

alpha_awareness <- psych::alpha(data %>% select(all_of(awareness_items)))

cat("\nCronbach's alpha coefficient:\n")
cat("Algorithmic awareness: ", round(alpha_awareness$total$raw_alpha, 2), "\n")

```

```{r proc social media}
# ---- PROCESS SOCIAL MEDIA USE VARIABLES ----

data <- data %>%
  # Recode missing values (99 -> NA) for all b12 items
  mutate(across(starts_with("b12"), ~ ifelse(. == 99, NA, .))) %>%
  
  # ---- Transform only e2_3_3 (Netflix) ----
  mutate(
    e2_3_3 = ifelse(e2_3_3 == 99, NA, e2_3_3),
    e2_3_3 = case_when(
    e2_3_3 %in% c(1, 2) ~ 1,  # Never done + Done 3 months ago
    e2_3_3 == 3 ~ 2,          # Once or three per month
    e2_3_3 == 4 ~ 3,          # All the weeks
    e2_3_3 == 5 ~ 4,          # Once a day or more
    e2_3_3 == 6 ~ 5,          # Once a day or more
    TRUE ~ NA_real_
    )
  ) %>%
  
  # Rename variables for clarity
  dplyr::rename(
    yt      = b12_1,
    fb      = b12_2,
    tw      = b12_3,
    ig      = b12_4,
    wsp     = b12_5,
    tiktok  = b12_6,
    netflix = e2_3_3
  ) %>%
  
  # Ensure all are numeric
  mutate(
    across(
      !c(gender, residence, region),  # exclude categorical variables
      ~ suppressWarnings(as.numeric(.))
    )
  )

# ---- PROCESS SOCIAL MEDIA BREADTH ----
# ---- MEDIA BREADTH INDEX ----
# Dichotomize use frequency for each platform (1 = weekly or more)
# Then sum across platforms to compute the total "media breadth" score

data$media_breadth <- data %>%
  # Temporarily recode use frequency for each social media platform
  mutate(across(
    c(yt, fb, tw, ig, wsp, tiktok, netflix),
    ~ case_when(
      . %in% c(4, 5) ~ 1,       # Frequent use (weekly or daily)
      . %in% c(1, 2, 3) ~ 0,    # Infrequent use
      TRUE ~ NA_integer_
    )
  )) %>%
  # Select only the recoded social media variables
  select(yt, fb, tw, ig, wsp, tiktok, netflix) %>%
  # Compute the number of frequently used platforms
  mutate(media_breadth = rowSums(., na.rm = FALSE)) %>%
  pull(media_breadth)

# data$media_breadth

data <- data %>%
  # Temporarily recode use frequency for each social media platform
  mutate(media_breadth_daily = case_when(
      media_breadth %in% c (5,6,7) ~ 2,       # Frequent use (weekly or daily)
      media_breadth %in% c(2,3,4) ~ 1,    # Non-frequent use
      media_breadth %in% c(0,1) ~ 0,    # Non use
      TRUE ~ NA_integer_
    )
  ) %>%
  mutate(media_breadth_daily = factor(media_breadth_daily,
                                      levels = c(0,1,2),
                                      labels = c("Non-daily user", 
                                                 "<5 daily user",
                                                 ">=5 daily user")))
```

# Methods

## Study design

This study draws on data from the National Digital Inclusion Survey conducted in Chile between August and October 2023, encompassing both rural and urban localities across the country. The survey was administered face-to-face by trained interviewers from a professional polling firm (Feedback).

The sample is probabilistic and representative of individuals aged 14 and older who are permanent residents of the selected locations. In urban areas, a stratified cluster sampling strategy was employed, with random selection of households within predefined blocks. In rural areas—characterized by smaller, dispersed populations—a random-route method was used, approximating a near-census coverage in each locality. One respondent per household was randomly selected for interview. The final analytic sample consists of 1,200 respondents, of whom 751 (62.6%) reside in urban areas and 449 (37.4%) in rural communities. The overall response rate (RR4), calculated following the American Association for Public Opinion Research guidelines, was 47.5%.

## Measures

*Algorithmic Awareness*

The dependent variable follows the Algorithmic Media Content Awareness (AMCA) scale (Zarouali et al., 2021), capturing respondents’ awareness that algorithms curate online content. It includes six items measuring: content filtering, behavioral dependence, and ethical implications (e.g., “Algorithms use my personal data, which has consequences for my online privacy”). Responses were rated on a five-point Likert scale (1 = Not at all aware to 5 = Completely aware) and averaged into a single scale (α \> .80). Higher scores indicate greater algorithmic awareness. Non-response value were codified as 1.

*Digital skills*

Digital skills were measured following van Deursen’s (CITA) multidimensional framework, encompassing four subdimensions derived from items in battery C3:

-   Operational skills — ability to manage basic technological operations such as installing apps or adjusting device settings \[6 items\].

-   Informational skills — capacity to search for, evaluate, and organize online information \[5 items\].

-   Social skills — ability to communicate, interact, and manage privacy on social media \[6 items\].

-   Creative skills — ability to create, edit, and share original digital content \[3 items\].

Each scales are sumative from dichotomical items phrased as know how to do (1). The scales have different number of items, so to conserve comparability, they were standardized (0–1). Higher values denote stronger digital competencies in each domain.

*Social media and platforms use*

Social media use was measured through a battery of seven items capturing the frequency of use of major platforms: Facebook, Instagram, YouTube, WhatsApp, TikTok, X (Twitter), and Netflix. Responses ranged from 1 (Never or less than once a month) to 5 (Several times a day). In addition to the individual frequency measures, we constructed a categorical variable of social media breadth, which represents the daily user engagement in overall platforms, ranging from High breadth (Daily use of five to seven social media), Medium breadth (Daily use of two to four social media) and Non-social media breadth (One or less daily use of social media).

*Familiar and Social resources*

Following the conceptualization of relational capital proposed in Are we there yet? (Correa et al., 2025), social and familial resources were included to capture the networked and dispositional factors that may facilitate digital engagement and awareness. Three indicators were employed. Innovative personality reflects an individual’s openness to experimentation, creativity, and adaptability in the use of technologies, measured through a battery of items assessing self-perceived willingness to explore and adopt new digital tools. Social network support represents the strength of respondents’ interpersonal ties and their access to assistance when facing technological or informational challenges—such as having friends, family members, or community peers who can provide guidance or share resources. Finally, number of children in the household (childs) serves as a proxy for family responsibilities and time constraints that can affect the capacity to engage with digital technologies. 

*Sociodemographic Controls*

Control variables included are age (continuos, in years), gender (0 = male; 1 = female), educational status (1 = primary or less, to 5 = college or more), household income (9 values ordinal scale with ranges adapted to number of members) and the type of residence, coded as urban or rural following the national Statistics Institute's classification.

```{r}
#| lbl: descriptives
#| tbl-cap: Descriptive table

# ---- Variables to summarize ----
model_vars <- c(
  "algorithmic_awareness", 
  "age", "gender", "nse", "residence",
  "innovative_personality", "soc_net", "childs",
  "tech_operational_skills", "tech_informative_skills", 
  "tech_social_skills", "tech_creative_skills",
  "yt", "fb", "tw", "ig", "wsp", "tiktok", "netflix",
  "media_breadth_daily"
)

data <- data%>%
  mutate(gender = as_factor(gender),
         residence = as_factor(residence))
# ---- Predefine item sets for Cronbach’s alpha ----
index_items <- list(
  algorithmic_awareness   = grep("^d2_", names(data), value = TRUE),
  tech_operational_skills = grep("^c3_1_", names(data), value = TRUE),
  tech_informative_skills = grep("^c3_2_", names(data), value = TRUE),
  tech_social_skills      = grep("^c3_3_", names(data), value = TRUE),
  tech_creative_skills    = grep("^c3_4_", names(data), value = TRUE),
  innovative_personality  = grep("^p1_", names(data), value = TRUE),
  soc_net                 = grep("^s1_", names(data), value = TRUE)
)

# ---- Compute Cronbach’s alpha for each index ----
alpha_values <- sapply(index_items, function(vars) {
  vars <- intersect(vars, names(data))
  if (length(vars) > 1) {
    round(psych::alpha(data[, vars], check.keys = TRUE)$total$raw_alpha, 2)
  } else {
    NA
  }
})

# ---- Build descriptive table ----
desc_table <- lapply(model_vars, function(v){
  x <- data[[v]]
  
  # Detect variable type
  if (is.factor(x) || v %in% c("gender", "residence", "media_breadth_daily")) {
    tab <- table(x, useNA = "ifany")
    pct <- round(prop.table(tab) * 100, 1)
    desc <- paste0(names(tab), " (", as.vector(tab), ", ", as.vector(pct), "%)", collapse = "; ")
    v_type <- "Categorical"
  } else if (is.numeric(x)) {
    desc <- paste0(round(mean(x, na.rm = TRUE), 2), " (", round(sd(x, na.rm = TRUE), 2), ")")
    v_type <- "Numeric"
  } else {
    desc <- NA
    v_type <- "Other"
  }
  
  # Add alpha if relevant
  alpha_val <- ifelse(v %in% names(alpha_values), alpha_values[v], NA)
  
  data.frame(
    Variable = v,
    Type = v_type,
    Description = desc,
    N_observed = sum(!is.na(x)),
    N_missing = sum(is.na(x)),
    Cronbach_alpha = alpha_val,
    stringsAsFactors = FALSE
  )
}) %>% bind_rows()

# ---- Format with flextable ----
ft_final <- flextable(desc_table) %>%
  autofit() %>%
  set_header_labels(
    Variable = "Variable",
    Type = "Type",
    Description = "Description (Mean±SD or categories)",
    N_observed = "N Observed",
    N_missing = "N Missing",
    Cronbach_alpha = "Cronbach’s α"
  ) %>%
  theme_booktabs() %>%
  align(align = "center", part = "all")

# ---- Display table ----
ft_final

# ---- Optionally export to Word ----
# save_as_docx(ft_final, path = "Descriptive_Table.docx")

```

## Analytical strategy

We estimated a series of four nested linear regression models (OLS) to examine the increasing explanatory blocks of algorithmic awareness. The main independent variables were the four dimensions of digital skills and the six social media use indicators, controlling for demographical variables. All continuous variables were mean-centered prior to analysis to facilitate interpretation. Robust standard errors were computed to account for potential heteroskedasticity.

Model diagnostics confirmed the absence of multicollinearity (all VIF \< 2.5) and normal distribution of residuals. Analyses were conducted using R 4.4.2 software. Marginal effects and standardized coefficients are reported for comparability. Statistical significance was set at p \< .05.

# Results

## Correlation matrix

The correlation matrix (Table X) reveals consistent and theoretically coherent associations among the main study variables. Algorithmic awareness is strongly and positively correlated with all four dimensions of digital skills—particularly operational (r ≈ .61) and social (r ≈ .58) skills—while showing moderate associations with socioeconomic status (r ≈ .34) and social network support (r ≈ .29). The breadth of social media use exhibits a smaller but significant positive correlation with algorithmic awareness (r ≈ .30), suggesting that greater platform diversity is modestly linked to higher awareness levels. Age correlates negatively with both digital skills and awareness, whereas NSE and digital competencies display the strongest internal coherence across measures. Overall, the correlation structure supports the proposed analytical model, highlighting the central role of digital skills in the formation of algorithmic awareness.

```{r corr}
#| lbl: corr-matrix
#| tbl-cap: Correlation matrix
# ---- CORRELATION MATRIX ----

# ---- CORRELATION VARIABLES SELECTION ----

# Convert categorical variables (gender, residence) to numeric for correlation
data <- data %>%
  mutate(
    gender_num    = ifelse(gender == "Female", 1, 0),
    residence_num = ifelse(residence == "Rural", 1, 0)
  )

# Select variables for correlation matrix
corr_vars <- data %>%
  select(
    algorithmic_awareness,
    age,
    gender_num,
    nse,
    residence_num,
    innovative_personality,
    soc_net,
    childs,
    tech_operational_skills,
    tech_informative_skills,
    tech_social_skills,
    tech_creative_skills,
    yt, fb, tw, ig, wsp, tiktok, netflix,
    media_breadth
  )


# Compute correlations with p-values
corr_test <- Hmisc::rcorr(as.matrix(corr_vars), type = "pearson")

# Extract correlation coefficients and p-values
r <- round(corr_test$r, 2)
p <- corr_test$P

# Combine correlation and p-value into one string
corr_table <- matrix(
  paste0(r, "\n(", ifelse(p < 0.001, "<.001", round(p, 3)), ")"),
  ncol = ncol(r)
)
colnames(corr_table) <- colnames(r)
rownames(corr_table) <- rownames(r)

# Convert to data frame for printing
corr_table_df <- as.data.frame(corr_table)

# --- Usa tu mismo código para preparar la tabla ---
# (Selección de variables, cálculo de corrs, etc.)

# Solo cambia el paso final de knitr::kable a DT::datatable
DT::datatable(
  corr_table_df,
  caption = "Pearson Correlation Matrix with p-values",
  options = list(
    scrollX = TRUE,  # ¡Esta es la opción clave para el desplazamiento horizontal!
    pageLength = 10, # Controla cuántas filas se muestran por página
    columnDefs = list(list(className = 'dt-center', targets = "_all")) # Centrar texto
  ),
  class = 'cell-border stripe' # Estilo visual
)
```

## Linear Models

Four hierarchical linear models were specified to assess the explanatory power of demographic factors, social and family resources, social media use and breadth, and digital skills on algorithmic awareness. As media breadth was constructed with the different social media variables, they were introduced by separate in the models to avoid multicolinearity. Diagnostic tests were performed to ensure the validity of the estimations, confirming that none of the predictors presented a Variance Inflation Factor (VIF) greater than 3.5. This indicates that multicollinearity is not a concern, reinforcing the robustness and interpretability of the coefficients.

The assessment of model fit shows that Model 4, which incorporates digital skills in addition to demographic, social resource, and media variables, provides the most comprehensive and robust explanation for the variance in algorithmic awareness. This full model displays the highest adjusted R² (R² adj. = .558) and the lowest Akaike Information Criterion (AIC = 171.033), indicating an optimal balance between explanatory power and parsimony.

Model 1 (Demographics) demonstrates that socioeconomic status (β = 0.09, p < .001) and residence in rural areas (β = −0.09, p < .001) are significant predictors of algorithmic awareness, while gender differences are non-significant. Age exhibits a small but consistent negative effect (β = −0.01, p < .001), suggesting lower algorithmic awareness among older respondents.

Model 2 (Social and Family Resources) adds innovative personality, social network support, and number of children in the household. The inclusion of these variables slightly improves model fit, though the overall pattern remains stable. Social network support shows a positive and significant association with algorithmic awareness (β = 0.02, p < .001), while the number of children is negatively associated (β = −0.03, p < .01). The effect of innovative personality is positive but not statistically significant.

Model 3 (Media breadth) add the social media breadth qualitative construct. Medium and High breadth present advantages over Non-social media breadth (β = 0.06, p < .05 and β = 0.16, p < .01 respectively).

Model 4 (Social Media Use) incorporates the frequency of use of seven platforms—YouTube, Facebook, Twitter (X), Instagram, WhatsApp, TikTok, and Netflix. Although this addition only marginally increases the model’s explanatory power, several noteworthy patterns emerge. The use of Twitter (β = 0.04, p < .001) and Netflix (β = 0.03, p < .01) is positively associated with algorithmic awareness, whereas Facebook shows a negative relationship (β = −0.02, p < .05).

Model 5 (Digital Skills with Media breadth) introduces the four dimensions of digital competence—operational, informative, social, and creative skills—based on van Deursen’s typology. The inclusion of these competencies substantially improves model fit, underscoring their pivotal role in shaping algorithmic awareness. Operational skills (β = 0.20, p < .001) and creative skills (β = 0.16, p < .001) emerge as the strongest predictors, followed by social skills (β = 0.07, p < .05) and informative skills (β = 0.05, n.s.). Once these skills are included, most demographic and social variables lose significance, indicating that the effects of socioeconomic position, social capital and media breadth are largely mediated by the level of digital competence. 

Model 6 (Digital Skills with Social media frequency use) show similar effects as Model 5 on digital skills dimensions, and demonstrate that with this controls, the different social media use maintain relatively equal effects previously presented on Model 4.

In sum, the sequential modeling confirms that digital skills constitute the central explanatory factor for algorithmic awareness. While social resources and the diversity of social media use contribute marginally, their influence is secondary to users’ actual digital competencies. The progressive attenuation of demographic effects across models reinforces the notion that algorithmic awareness is primarily a matter of digital literacy, rather than demographic privilege or media exposure alone.

```{r models}
#| lbl: models
#| tbl-cap: Summary linear models
# ---- REGRESSION MODELS ----

# Ensure categorical variables are properly set
data <- data %>%
  mutate(
    gender = factor(gender, levels = c("Male", "Female")),
    residence = factor(residence, levels = c("Urban", "Rural")),
    media_breadth_daily = factor(media_breadth_daily, levels = c("Non-daily user", "<5 daily user", ">=5 daily user"))
  )

# ---- MODEL 1: Demographics only ----
model1 <- lm(
  algorithmic_awareness ~ age + gender + nse + residence,
  data = data
)

# ---- MODEL 2: Adds social and family resources ----
model2 <- lm(
  algorithmic_awareness ~ age + gender + nse + residence +
    innovative_personality + soc_net + childs,
  data = data
)

# ---- MODEL 3: Social media breadth ----
model3 <- lm(
  algorithmic_awareness ~ age + gender + nse + residence +
    innovative_personality + soc_net + childs +
    media_breadth_daily,
  data = data
)

# ---- MODEL 4: Adds social media use ----
model4 <- lm(
  algorithmic_awareness ~ age + gender + nse + residence +
    innovative_personality + soc_net + childs +
    yt + fb + tw + ig + wsp + tiktok + netflix,
  data = data
)

# ---- MODEL 5 & 6: Adds digital skills ----
model5 <- lm(
  algorithmic_awareness ~ age + gender + nse + residence +
    innovative_personality + soc_net + childs +
    media_breadth_daily +
    tech_operational_skills + tech_informative_skills +
    tech_social_skills + tech_creative_skills,
  data = data
)

model6 <- lm(
  algorithmic_awareness ~ age + gender + nse + residence +
    innovative_personality + soc_net + childs +
    yt + fb + tw + ig + wsp + tiktok + netflix + 
    tech_operational_skills + tech_informative_skills +
    tech_social_skills + tech_creative_skills,
  data = data
)

# ---- Apply robust standard errors (HC3) ----
#cov1 <- vcovHC(model1, type = "HC3")
#cov2 <- vcovHC(model2, type = "HC3")
#cov3 <- vcovHC(model3, type = "HC3")
#cov4 <- vcovHC(model4, type = "HC3")

# ---- Display models with variable labels ----
tab_model(
  model1, model2, model3, model4, model5, model6,
  collapse.se = TRUE,      
  show.ci = FALSE,
  show.aic = TRUE,
  show.r2 = TRUE,
  show.fstat = TRUE,
  p.style = "stars",
  dv.labels = c(
    "Model 1: Demographics",
    "Model 2: + Social Resources",
    "Model 3: + Media breadth",
    "Model 4: + Social Media Use",
    "Model 5: + Digital Skills (Media breadth)",
    "Model 6: + Digital Skills (Media use)"
  ),
  title = "Linear Regression Models Predicting Algorithmic Awareness",
  
  # ---- Variable labels ----
  pred.labels = c(
    "Intercept",
    "Age",
    "Gender (ref: Male)",
    "Socioeconomic Status (SES)",
    "Rural Residence",
    "Innovative Personality",
    "Social Network Support",
    "Number of Children in Household",
    "Medium breadth (Ref: Non-social media breadth)",
    "High breadth (Ref: Non-social media breadth)",
    "YouTube Use",
    "Facebook Use",
    "X (Twitter) Use",
    "Instagram Use",
    "WhatsApp Use",
    "TikTok Use",
    "Netflix Use",
    "Operational Skills",
    "Informative Skills",
    "Social Skills",
    "Creative Skills"
  )
)
```


## VIF

VIF values for all predictors in Model 4 remain below acceptable thresholds (all < 5, with social media breadth being highest). Residual inspection suggests approximate normality and homoskedastic behavior.

*media_breadth_daily: only -.10 significant >= daily use. 3.5 VIF

*media_breadth_weekly: non-significant differences between groups. 5.0 VIF

```{r}
#| lbl: vif
#| tbl-cap: VIF test model 3
vif(model4)|>kable()
```
