---
title: "ICA 2026"
author: "Teresa Correa, Catalina Farías & Nicolás Tobar"
date: 14-11-2023
format:
  html:
    code-fold: true
execute: 
  error: false
  warning: false
  message: false
editor: visual
---

```{r intro}
# ---- PACKAGE MANAGEMENT ----
# This block loads (and installs if necessary) all required packages
if (!require("pacman")) install.packages("pacman")

pacman::p_load(
  tidyverse,    # data wrangling (dplyr, ggplot2, etc.)
  haven,        # import SPSS/Stata/SAS data
  labelled,     # manage variable and value labels
  psych,        # reliability tests (Cronbach's alpha)
  sjlabelled,   # labeling utilities compatible with tidyverse
  car,          # regression diagnostics (VIF, etc.)
  lmtest,       # regression tests
  sandwich,     # lm specifications
  Hmisc,        # Correlation matrix
  scales,       # normalization and rescaling
  dplyr,        # ensure dplyr functions are active
  psych,        # cronbach alpha
  readr,        # reading csv or txt data
  tidyr,        # data tidying
  stringr,      # string handling
  sjPlot,       # Plot analysis
  ggplot2,      # data visualization
  knitr,        # Markdown knit
  KableExtra,    # Personalize design knit
  flextable     # export tables 
)

#Open data
load("~/GitHub/milenio_nudos/2023_digital_inclusion/01_input/02_proc_data/digital_inclusion_2023.RData")
```

```{r proc demographics}
# ---- SOCIODEMOGRAPHIC VARIABLES ----
data <- data %>%
  mutate(
    # Gender: 0 = male, 1 = female
    a1 = ifelse(a1 == 2, 1,
         ifelse(a1 == 1, 0, NA)),

    gender = factor(a1,
                    levels = c(0, 1),
                    labels = c("Male", "Female")),
    
    # Change age variable name
    age = a2,
    
    # Type of residence: 1 = urban, 2 = ral
    residence = case_when(
      tipo_zona == 1 ~ "Urban",
      tipo_zona == 2 ~ "Rural",
      TRUE ~ NA_character_
    ),
    residence = factor(residence, levels = c("Urban", "Rural"))
  )

# Innovative personality
innovative_variables_2023 <- data %>% dplyr::select(starts_with("f2_"))%>%
                             mutate(across(everything(),~case_when(.==1~4,
                                                          .==2~3,
                                                          .==3~2,
                                                          .==4~1,
                                                          TRUE ~ NA_real_)))

data$innovative_personality <- innovative_variables_2023 %>% 
  mutate_all(as.integer)%>%
  rowMeans(na.rm=T)

#Social network
data$soc_net <- data %>% 
  dplyr::select(starts_with("f6_")) %>%
  mutate_all(as.integer) %>%
  mutate(across(everything(),~case_when(.==2~0,
                                        .==1~1,
                                        TRUE~NA_real_)))%>%
  rowSums(na.rm=T)

#Childs in house (taken from raw_data)
raw_2023 <- read_sav("../01_input/01_raw_data/2023_survey_raw.sav") %>% 
  janitor::clean_names()

data$childs <- raw_2023 %>% 
  dplyr::select(starts_with("edad")) %>%
  mutate_all(~case_when(.<=18~1,.>18~0,TRUE~NA_real_)) %>%
  rowSums(.,na.rm = T)%>%as.numeric()

```

```{r proc digital skills}

# ---- DIGITAL SKILLS INDICES (van Deursen, 2014; 2020) ----
# Each subscale is built from items in battery C3 following your structure.

# Define item groups
operational_items <- c("c3_1_1", "c3_1_2", "c3_1_3", "c3_1_4", "c3_1_5", "c3_1_6")
informative_items <- c("c3_2_1", "c3_2_2", "c3_2_3", "c3_2_4", "c3_2_5")
social_items      <- c("c3_3_1", "c3_3_2", "c3_3_3", "c3_3_4", "c3_3_5", "c3_3_6")
creative_items    <- c("c3_4_1", "c3_4_2", "c3_4_3")

# ---- Ensure C3 items are numeric ----
data <- data %>%
  # Convertir items c3 a 0/1 y reemplazar 99 por NA
  mutate(across(starts_with("c3"), ~ case_when(
    . == 1 ~ 1,
    . == 2 ~ 0,
    . == 99 ~ NA_integer_,
    TRUE ~ NA_integer_
  ))) %>%
  # Asegurar que las sub-dimensiones sean numéricas
  mutate(across(all_of(c(operational_items, informative_items, social_items, creative_items)), ~ as.numeric(.)))


# ---- SUMMATIVE INDICES (raw sums) with NA-if-all-missing protection ----
data <- data %>%
  mutate(
    # Operational (sum of c3_1_*)
    op_n = rowSums(!is.na(select(., all_of(operational_items)))),
    op_sum = rowSums(select(., all_of(operational_items)), na.rm = TRUE),
    tech_operational_skills_raw = if_else(op_n == 0, NA_real_, op_sum),

    # Informative (sum of c3_2_*)
    inf_n = rowSums(!is.na(select(., all_of(informative_items)))),
    inf_sum = rowSums(select(., all_of(informative_items)), na.rm = TRUE),
    tech_informative_skills_raw = if_else(inf_n == 0, NA_real_, inf_sum),

    # Social (sum of c3_3_*)
    soc_n = rowSums(!is.na(select(., all_of(social_items)))),
    soc_sum = rowSums(select(., all_of(social_items)), na.rm = TRUE),
    tech_social_skills_raw = if_else(soc_n == 0, NA_real_, soc_sum),

    # Creative (sum of c3_4_*)
    cre_n = rowSums(!is.na(select(., all_of(creative_items)))),
    cre_sum = rowSums(select(., all_of(creative_items)), na.rm = TRUE),
    tech_creative_skills_raw = if_else(cre_n == 0, NA_real_, cre_sum)
  )

# ---- NORMALIZATION to 0-1 (observed min-max) ----
# keep normalize function (observed min-max)
normalize <- function(x) (x - min(x, na.rm = TRUE)) / 
                         (max(x, na.rm = TRUE) - min(x, na.rm = TRUE))

data <- data %>%
  mutate(
    tech_operational_skills = normalize(tech_operational_skills_raw),
    tech_informative_skills = normalize(tech_informative_skills_raw),
    tech_social_skills      = normalize(tech_social_skills_raw),
    tech_creative_skills    = normalize(tech_creative_skills_raw)
  )

# ---- RELIABILITY CHECK (OPTIONAL) ----
# Cronbach’s alpha for each subscale (recommended for reporting)
#library(psych)

#alpha_operational <- psych::alpha(data %>% select(all_of(operational_items)))
#alpha_informative <- psych::alpha(data %>% select(all_of(informative_items)))
#alpha_social      <- psych::alpha(data %>% select(all_of(social_items)))
#alpha_creative    <- psych::alpha(data %>% select(all_of(creative_items)))

#cat("\nCronbach's alpha coefficients:\n")
#cat("Operational skills: ", round(alpha_operational$total$raw_alpha, 2), "\n")
#cat("Informative skills: ", round(alpha_informative$total$raw_alpha, 2), "\n")
#cat("Social skills: ", round(alpha_social$total$raw_alpha, 2), "\n")
#cat("Creative skills: ", round(alpha_creative$total$raw_alpha, 2), "\n")

```

```{r proc algorithmic awareness}
# ---- ALGORITHMIC AWARENESS INDEX (MEAN SCALE) ----
# Based on items from battery D2 (Algorithmic Media Content Awareness - AMCA)

# 1. Convert all D2 items to numeric
data <- data %>%
  mutate(across(starts_with("d2"), as.numeric))%>%
  mutate(across(starts_with("d2"), ~ ifelse(. == 99, 1, .)))

# 2. Compute the mean index for algorithmic awareness
#    The index represents the average awareness level across all D2 items
data <- data %>%
  mutate(
    algorithmic_awareness = rowMeans(select(., starts_with("d2")), na.rm = TRUE)
  )

# 3. Normalize to 0–1 range (optional, for comparability with other indices)
normalize <- function(x) (x - min(x, na.rm = TRUE)) / 
                         (max(x, na.rm = TRUE) - min(x, na.rm = TRUE))

data <- data %>%
  mutate(
    algorithmic_awareness = normalize(algorithmic_awareness)
  )

# 4. Reliability check (Cronbach’s alpha)
awareness_items <- names(select(data, starts_with("d2")))

alpha_awareness <- psych::alpha(data %>% select(all_of(awareness_items)))

cat("\nCronbach's alpha coefficient:\n")
cat("Algorithmic awareness: ", round(alpha_awareness$total$raw_alpha, 2), "\n")

```

```{r proc social media}
# ---- PROCESS SOCIAL MEDIA USE VARIABLES ----

data <- data %>%
  # Recode missing values (99 -> NA) for all b12 items
  mutate(across(starts_with("b12"), ~ ifelse(. == 99, NA, .))) %>%
  
  # ---- Transform only e2_3_3 (Netflix) ----
  mutate(
    e2_3_3 = ifelse(e2_3_3 == 99, NA, e2_3_3),
    e2_3_3 = case_when(
    e2_3_3 %in% c(1, 2) ~ 1,  # Never done + Done 3 months ago
    e2_3_3 == 3 ~ 2,          # Once or three per month
    e2_3_3 == 4 ~ 3,          # All the weeks
    e2_3_3 == 5 ~ 4,          # Once a day or more
    e2_3_3 == 6 ~ 5,  # Once a day or more
    TRUE ~ NA_real_
    )
  ) %>%
  
  # Rename variables for clarity
  dplyr::rename(
    yt      = b12_1,
    fb      = b12_2,
    tw      = b12_3,
    ig      = b12_4,
    wsp     = b12_5,
    tiktok  = b12_6,
    netflix = e2_3_3
  ) %>%
  
  # Ensure all are numeric
  mutate(
    across(
      !c(gender, residence, region),  # exclude categorical variables
      ~ suppressWarnings(as.numeric(.))
    )
  )

# ---- PROCESS SOCIAL MEDIA BREADTH ----
# ---- MEDIA BREADTH INDEX ----
# Dichotomize use frequency for each platform (1 = weekly or more)
# Then sum across platforms to compute the total "media breadth" score

data$media_breadth <- data %>%
  # Temporarily recode use frequency for each social media platform
  mutate(across(
    c(yt, fb, tw, ig, wsp, tiktok, netflix),
    ~ case_when(
      . %in% c(4, 5) ~ 1,       # Frequent use (weekly or daily)
      . %in% c(1, 2, 3) ~ 0,    # Infrequent use
      TRUE ~ NA_integer_
    )
  )) %>%
  # Select only the recoded social media variables
  select(yt, fb, tw, ig, wsp, tiktok, netflix) %>%
  # Compute the number of frequently used platforms
  mutate(media_breadth = rowSums(., na.rm = FALSE)) %>%
  pull(media_breadth)

```

# Methods

## Study design

This study draws on data from the National Digital Inclusion Survey conducted in Chile between August and October 2023, encompassing both rural and urban localities across the country. The survey was administered face-to-face by trained interviewers from a professional polling firm (Feedback).

The sample is probabilistic and representative of individuals aged 14 and older who are permanent residents of the selected locations. In urban areas, a stratified cluster sampling strategy was employed, with random selection of households within predefined blocks. In rural areas—characterized by smaller, dispersed populations—a random-route method was used, approximating a near-census coverage in each locality. One respondent per household was randomly selected for interview. The final analytic sample consists of 1,200 respondents, of whom 751 (62.6%) reside in urban areas and 449 (37.4%) in rural communities. The overall response rate (RR4), calculated following the American Association for Public Opinion Research guidelines, was 47.5%.

## Measures

*Algorithmic Awareness*

The dependent variable follows the Algorithmic Media Content Awareness (AMCA) scale (Zarouali et al., 2021), capturing respondents’ awareness that algorithms curate online content. It includes three items measuring: content filtering, behavioral dependence, and ethical implications (e.g., “Algorithms use my personal data, which has consequences for my online privacy”). Responses were rated on a five-point Likert scale (1 = Not at all aware to 5 = Completely aware) and averaged into a single scale (α \> .80). Higher scores indicate greater algorithmic awareness. Non-response value were codified as 1.

*Digital skills*

Digital skills were measured following van Deursen’s (CITA) multidimensional framework, encompassing four subdimensions derived from items in battery C3:

-   Operational skills — ability to manage basic technological operations such as installing apps or adjusting device settings \[6 items\].

-   Informational skills — capacity to search for, evaluate, and organize online information \[5 items\].

-   Social skills — ability to communicate, interact, and manage privacy on social media \[6 items\].

-   Creative skills — ability to create, edit, and share original digital content \[3 items\].

Each scales are sumative from dichotomical items phrased as know how to do (1). The scales have different number of items, so to conserve comparability, they were standardized (0–1). Higher values denote stronger digital competencies in each domain.

*Social media and platforms use*

Social media use was measured through a battery of seven items capturing the frequency of use of major platforms: Facebook, Instagram, YouTube, WhatsApp, TikTok, X (Twitter), and Netflix. Responses ranged from 1 (Never or less than once a month) to 5 (Several times a day). In addition to the individual frequency measures, we constructed a composite scale of social media breadth, which represents the number of platforms each respondent reported using at least weekly. This additive indicator captures the overall diversity of social media engagement, ranging from 0 (no platforms used weekly or more) to 7 (all platforms used weekly or more).

*Sociodemographic Controls*

Control variables included are age (continuos, in years), gender (0 = male; 1 = female), educational status (1 = primary or less, to 5 = college or more), household income (9 values ordinal scale with ranges adapted to number of members) and the type of residence, coded as urban or rural following the national Statistics Institute's classification.

```{r}
#| lbl: descriptives
#| tbl-cap: Descriptive table

# ---- Variables to summarize ----
model_vars <- c(
  "algorithmic_awareness", 
  "age", "gender", "nse", "residence",
  "innovative_personality", "soc_net", "childs",
  "tech_operational_skills", "tech_informative_skills", 
  "tech_social_skills", "tech_creative_skills",
  "yt", "fb", "tw", "ig", "wsp", "tiktok", "netflix",
  "media_breadth"
)

data <- data%>%
  mutate(gender = as_factor(gender),
         residence = as_factor(residence))
# ---- Predefine item sets for Cronbach’s alpha ----
index_items <- list(
  algorithmic_awareness   = grep("^d2_", names(data), value = TRUE),
  tech_operational_skills = grep("^c3_1_", names(data), value = TRUE),
  tech_informative_skills = grep("^c3_2_", names(data), value = TRUE),
  tech_social_skills      = grep("^c3_3_", names(data), value = TRUE),
  tech_creative_skills    = grep("^c3_4_", names(data), value = TRUE),
  innovative_personality  = grep("^p1_", names(data), value = TRUE),
  soc_net                 = grep("^s1_", names(data), value = TRUE)
)

# ---- Compute Cronbach’s alpha for each index ----
alpha_values <- sapply(index_items, function(vars) {
  vars <- intersect(vars, names(data))
  if (length(vars) > 1) {
    round(psych::alpha(data[, vars], check.keys = TRUE)$total$raw_alpha, 2)
  } else {
    NA
  }
})

# ---- Build descriptive table ----
desc_table <- lapply(model_vars, function(v){
  x <- data[[v]]
  
  # Detect variable type
  if (is.factor(x) || v %in% c("gender", "residence")) {
    tab <- table(x, useNA = "ifany")
    pct <- round(prop.table(tab) * 100, 1)
    desc <- paste0(names(tab), " (", as.vector(tab), ", ", as.vector(pct), "%)", collapse = "; ")
    v_type <- "Categorical"
  } else if (is.numeric(x)) {
    desc <- paste0(round(mean(x, na.rm = TRUE), 2), " (", round(sd(x, na.rm = TRUE), 2), ")")
    v_type <- "Numeric"
  } else {
    desc <- NA
    v_type <- "Other"
  }
  
  # Add alpha if relevant
  alpha_val <- ifelse(v %in% names(alpha_values), alpha_values[v], NA)
  
  data.frame(
    Variable = v,
    Type = v_type,
    Description = desc,
    N_observed = sum(!is.na(x)),
    N_missing = sum(is.na(x)),
    Cronbach_alpha = alpha_val,
    stringsAsFactors = FALSE
  )
}) %>% bind_rows()

# ---- Format with flextable ----
ft_final <- flextable(desc_table) %>%
  autofit() %>%
  set_header_labels(
    Variable = "Variable",
    Type = "Type",
    Description = "Description (Mean±SD or categories)",
    N_observed = "N Observed",
    N_missing = "N Missing",
    Cronbach_alpha = "Cronbach’s α"
  ) %>%
  theme_booktabs() %>%
  align(align = "center", part = "all")

# ---- Display table ----
ft_final

# ---- Optionally export to Word ----
# save_as_docx(ft_final, path = "Descriptive_Table.docx")

```

## Analytical strategy

We estimated a series of linear regression models to examine the predictors of algorithmic awareness. The main independent variables were the four dimensions of digital skills and the six social media use indicators, controlling for demographical variables. All continuous variables were mean-centered prior to analysis to facilitate interpretation. Robust standard errors were computed to account for potential heteroskedasticity.

Model diagnostics confirmed the absence of multicollinearity (all VIF \< 2.5) and normal distribution of residuals. Analyses were conducted using R 4.4.2 software. Marginal effects and standardized coefficients are reported for comparability. Statistical significance was set at p \< .05.

# Results

## Correlation matrix

```{r corr}
#| lbl: corr-matrix
#| tbl-cap: Correlation matrix
# ---- CORRELATION MATRIX ----

# ---- CORRELATION VARIABLES SELECTION ----

# Convert categorical variables (gender, residence) to numeric for correlation
data <- data %>%
  mutate(
    gender_num    = ifelse(gender == "Female", 1, 0),
    residence_num = ifelse(residence == "Rural", 1, 0)
  )

# Select variables for correlation matrix
corr_vars <- data %>%
  select(
    algorithmic_awareness,
    age,
    gender_num,
    nse,
    residence_num,
    innovative_personality,
    soc_net,
    childs,
    tech_operational_skills,
    tech_informative_skills,
    tech_social_skills,
    tech_creative_skills,
    yt, fb, tw, ig, wsp, tiktok, netflix,
    media_breadth
  )


# Compute correlations with p-values
corr_test <- Hmisc::rcorr(as.matrix(corr_vars), type = "pearson")

# Extract correlation coefficients and p-values
r <- round(corr_test$r, 2)
p <- corr_test$P

# Combine correlation and p-value into one string
corr_table <- matrix(
  paste0(r, "\n(", ifelse(p < 0.001, "<.001", round(p, 3)), ")"),
  ncol = ncol(r)
)
colnames(corr_table) <- colnames(r)
rownames(corr_table) <- rownames(r)

# Convert to data frame for printing
corr_table_df <- as.data.frame(corr_table)

# --- Usa tu mismo código para preparar la tabla ---
# (Selección de variables, cálculo de corrs, etc.)

# Solo cambia el paso final de knitr::kable a DT::datatable
DT::datatable(
  corr_table_df,
  caption = "Pearson Correlation Matrix with p-values",
  options = list(
    scrollX = TRUE,  # ¡Esta es la opción clave para el desplazamiento horizontal!
    pageLength = 10, # Controla cuántas filas se muestran por página
    columnDefs = list(list(className = 'dt-center', targets = "_all")) # Centrar texto
  ),
  class = 'cell-border stripe' # Estilo visual
)
```

## Linear Models

Three nested models were then specified to assess the explanatory power of demographic factors, digital skills, and social media platform use. Diagnostic tests were performed to ensure the validity of the model, revealing that none of the variables exhibited a Variance Inflation Factor (VIF) greater than 5. This result is favorable, as it indicates that multicollinearity is not a concern, thereby strengthening the reliability and stability of the coefficient estimates.

The evaluation of the models' goodness-of-fit indicates that Model 2 offers the most parsimonious and robust explanation for the variance in algorithmic awareness. This model, which incorporates both demographic variables and digital skills, presents the highest adjusted R² value (R² adj. = .547) and the lowest Akaike Information Criterion (AIC = 161.033). The inclusion of social media usage variables in Model 3 did not improve the model's fit; rather, it weakened it slightly and reduced the number of observations.

The analysis of the coefficients from the superior Model 2 reveals the preponderant influence of digital skills as the most significant set of predictors. Specifically, operational skills (β = 0.31, p\<.001), creative skills (β = 0.16, p\<.001), and informative skills (β = 0.12, p\<.05) are all positively and significantly associated with greater algorithmic awareness. Regarding demographic variables, the effect of educational level, which was significant in Model 1 (β = 0.04, p\<.001), becomes non-significant in Model 2 (β = -0.00, n.s.) after the introduction of digital skills. This result suggests that the impact of formal education on algorithmic awareness is mediated by the development of digital competencies. Furthermore, household income (β = 0.03, p\<.01) and residence in urban areas (β = -0.06, p\<.01) maintain a positive and significant association. Age presents a small but significant negative relationship (β = -0.00, p\<.001).

Although Model 3 demonstrated a weaker fit, its coefficients offer relevant nuances regarding platform use. The use of Twitter (β = 0.04, p\<.001) and Netflix (β = 0.04, p\<.001) is positively associated with algorithmic awareness, whereas the use of Facebook correlates negatively (β = -0.02, p\<.05). The use of other platforms such as YouTube, Instagram, or TikTok yielded no statistically significant effects. In conclusion, the findings demonstrate that digital skills are the central predictor of algorithmic awareness, surpassing the importance of traditional sociodemographic factors and the usage patterns of specific social platforms.

```{r models}
#| lbl: models
#| tbl-cap: Summary linear models
# ---- REGRESSION MODELS ----

# Ensure categorical variables are properly set
data <- data %>%
  mutate(
    gender = factor(gender, levels = c("Male", "Female")),
    residence = factor(residence, levels = c("Urban", "Rural"))
  )

# ---- MODEL 1: Demographics only ----
model1 <- lm(
  algorithmic_awareness ~ age + gender + nse + residence,
  data = data
)

# ---- MODEL 2: Adds social and family resources ----
model2 <- lm(
  algorithmic_awareness ~ age + gender + nse + residence +
    innovative_personality + soc_net + childs,
  data = data
)

# ---- MODEL 3: Adds social media use ----
model3 <- lm(
  algorithmic_awareness ~ age + gender + nse + residence +
    innovative_personality + soc_net + childs +
    yt + fb + tw + ig + wsp + tiktok + netflix + media_breadth,
  data = data
)

# ---- MODEL 4: Adds digital skills ----
model4 <- lm(
  algorithmic_awareness ~ age + gender + nse + residence +
    innovative_personality + soc_net + childs +
    yt + fb + tw + ig + wsp + tiktok + netflix + media_breadth +
    tech_operational_skills + tech_informative_skills +
    tech_social_skills + tech_creative_skills,
  data = data
)

# ---- Apply robust standard errors (HC3) ----
#cov1 <- vcovHC(model1, type = "HC3")
#cov2 <- vcovHC(model2, type = "HC3")
#cov3 <- vcovHC(model3, type = "HC3")
#cov4 <- vcovHC(model4, type = "HC3")

# ---- Display models with variable labels ----
tab_model(
  model1, model2, model3, model4,
  collapse.se = TRUE,      
  show.ci = FALSE,
  show.aic = TRUE,
  show.r2 = TRUE,
  show.fstat = TRUE,
  p.style = "stars",
  dv.labels = c(
    "Model 1: Demographics",
    "Model 2: + Social Resources",
    "Model 3: + Social Media Use",
    "Model 4: + Digital Skills"
  ),
  title = "Linear Regression Models Predicting Algorithmic Awareness",
  
  # ---- Variable labels ----
  pred.labels = c(
    "Intercept",
    "Age",
    "Gender (ref: Male)",
    "Socioeconomic Status (NSE)",
    "Residence (ref: Urban)",
    "Innovative Personality",
    "Social Network Support",
    "Number of Children in Household",
    "YouTube Use",
    "Facebook Use",
    "X (Twitter) Use",
    "Instagram Use",
    "WhatsApp Use",
    "TikTok Use",
    "Netflix Use",
    "Social Media Breadth",
    "Operational Skills",
    "Informative Skills",
    "Social Skills",
    "Creative Skills"
  )
)
```

# Revisión Multicoliniealidad (VIF)

```{r}
#| lbl: vif
#| tbl-cap: VIF test model 3
vif(model4)|>kable()
```
